Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-02-22 manuscript/manuscript.tex
More theoretical emphasis on the title
This is more of a theoretical paper with a bit of software than the
other way around.

Update my affiliation.

\title[Variable Density Tesseroids]{
    Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth
}
\author[S.R. Soler, A. Pesce, L. Uieda and M.E. Gimenez]{
    Santiado R. Soler$^{1,2}$, Agustina Pesce$^{1,2}$, Leonardo Uieda$^3$ and Mario E. Gimenez$^{1,2}$ \\
    $^1$CONICET, Argentina. e-mail: santiago.r.soler@gmail.com\\
    $^2$Instituto Geofísico Sismológico Volponi, Universidad Nacional de San Juan, Argentina\\
    $^3$Universidade do Estado do Rio de Janeiro, Rio de Janeiro, Brazil
    }

>>>>

\title[Variable Density Tesseroids]{
    Gravitational field calculation in spherical coordinates using variable densities in depth
}
\author[S.R. Soler, A. Pesce, L. Uieda and M.E. Gimenez]{
    Santiado R. Soler$^{1,2}$, Agustina Pesce$^{1,2}$, Leonardo Uieda$^3$ and Mario E. Gimenez$^{1,2}$ \\
    $^1$CONICET, Argentina. e-mail: santiago.r.soler@gmail.com\\
    $^2$Instituto Geofísico Sismológico Volponi, Universidad Nacional de San Juan, Argentina\\
    $^3$Department of Geology and Geophysics, SOEST, University of Hawai‘i at Manoa, Honolulu, Hawaii, USA
    }
